Correctness of a Set-based Algorithm for Computing Strongly Connected Components of a Graph

### 2022-08-17 Isabelle/document/root.tex
version of the theories submitted to the AFP

\title{A Set-based Algorithm for Computing Strongly Connected Components of a Graph}
\author{Stephan Merz and Vincent Trélat}
\maketitle

\begin{abstract}
  We prove the correctness of a sequential algorithm for computing strongly
  connected components (SCCs) of a graph due to Vincent Bloemen.
\end{abstract}

@@

>>>>

\title{Correctness of a Set-based Algorithm for Computing Strongly Connected Components of a Graph}
\author{Stephan Merz and Vincent Trélat}
\maketitle

\begin{abstract}
  We prove the correctness of a sequential algorithm for computing 
  maximal strongly connected components (SCCs) of a graph 
  due to Vincent Bloemen.
\end{abstract}

@@

\bibitem{lammich:gabow}
Peter Lammich.
\newblock Verified Efficient Implementation of Gabow's Strongly Connected Components Algorithm.
\newblock \emph{Archive of Formal Proofs}, 2014.
  \url{https://isa-afp.org/entries/Gabow_SCC.html}.
